### 2019-09-14 2019_neurips_vigil/intro.tex

Integration of vision and language in deep neural network models allows learning joint representations of objects, concepts, and relations.  In addition to multimodal learning, visual grounding of language is another opportunity that the AI community is excited about, especially in the context of Harnad's "symbol grounding problem" \cite{}.

@@

The ability to deal with time is also challenge for natural language processing (NLP), for example in question answering (QA) systems and in dialog.  The current QA solutions, in certain problem settings, can work around this challenge by processing the whole text input and reason over the text using attention or other mechanisms. For example the Memory Networks \cite{weston2015towards}, solves the bAbI reasoning task by processing all the facts at once, which reside in memory and available to provide answers. Similarly, in Visual Dialog~\cite{das2017visual} the system keeps the whole history of the dialog in memory.  In real-time dialog or video QA, there may not be such opportunity or the system may be forced to record the whole history which is not always feasible.  Video reasoning datasets such as SVQA (Synthetic Video Question Answering)~\cite{song2018explore}, TGIF-QA, and COG \cite{yang2018dataset} 
and 
Humans have the ability to selectively pay attention and store important items or events in memory based on their goals.  Working memory and episodic memory systems are responsible for this remarkable ability.

@@

visual reasoning~\cite{mogadala2019trends} - datasets such as COG~\cite{yang2018dataset} and 
SVQA (Synthetic Video Question Answering)~\cite{song2018explore}

ARISTO project~\cite{clark2019f} - based on RoBERTa~\cite{liu2019roberta} contextual word embeddings

transformer-based solutions~\cite{vaswani2017attention} using self-attention

“The current neural network approaches will find it difficult to determine which combinations of ‘later’, ‘earlier’, ‘more’, and ‘less’ constitute ‘increase’ and which constitute ‘decrease,'” Davis says. “Neural networks have no inherent idea of magnitude or of time.”
~\cite{davis2016write}

\begin{itemize}
\item bAbI:  MemNets~\cite{weston2014memory} have access to the whole story at once
\item the same goes to SoftPats~\cite{haurilet2019s} - they build graph per frame and then frame number is treated as one dimensions, so at the end the \textit{Traveler} can access all of them at the same time 
\item The paper~\cite{le2019learning} focuses on SVQA and TGIF-QA -  they access all frames at once, i.e. cut the video into clips, process each frame with CNNs and then aggregate feature representations of equal-size clips obtained by a temporal attention mechanism. So in fact the model has access to all frames all the time.
\end{itemize}
so the time aspect is really... not dealt with?

Additionally, in~\cite{song2018explore} the authors introduced a large-scale dataset caled SVQA (Synthetic Video Question Answering) consisting of (Total QA pairs: 83160/11760/23760 and Total Videos 8400/1200/2400).
As "using all frames is time-consuming. Thus we divide each video into clips (segments) of 16 frames, with 80\% overlap between successive clips (segments)" and "We extract feature from each clip and aggregate features of all clips from one video to form a sequential video representation." -- which means that they identified the problem that you "cannot extract features from all frames" at the beginning and pass that to the model. But instead of proposing a solution that will deal with the video on per-frame basis, they "cheated". ;)

IMPORTANT: \textbf{we do not have any explicit assumptions when it comes to number of frames/length of the movie/number of distractionts}, so there is no need for cutting video into cuts etc.

>>>>

Integration of vision and language in deep neural network models allows learning joint representations of objects, concepts, and relations.  In addition to multimodal learning, visual grounding of language is another opportunity that the AI community is excited about, especially in the context of Harnad's "symbol grounding problem" \cite{harnad2003symbol}.

@@

The ability to deal with time is a challenge also for natural language processing (NLP), for example in question answering (QA) systems and in dialog applications.  The current NLP solutions, in certain problem settings, can work around this challenge by processing the entire text input and reason over it using attention \cite{vaswani2017attention} or other mechanisms. For example, Memory Networks \cite{weston2015towards}, solves the bAbI reasoning task by processing the supporting facts all at once, which reside in memory and available to provide answers. Similarly, in Visual Dialog~\cite{das2017visual} the system keeps the whole history of the dialog in memory.  In real-time dialog or video QA, there may not be such opportunity or the system may be forced to record the whole history which is not always feasible.  Video reasoning datasets such as SVQA (Synthetic Video Question Answering)~\cite{song2018explore} and COG \cite{yang2018dataset} have limited number of frames (e.g. 4-16 frames), and therefore manageable by the neural net models to process and represent all of the visual information. According to\cite{song2018explore} the authors extracted visual features from each clip and aggregated features of all clips from one video to form a sequential video representation.
These solutions may demonstrate high accuracy and apply to specific problems, however, generalization to arbitrary length video sequences will be problematic.  Such approaches also differ from the human cognitive strategies.  Humans have the ability to selectively pay attention and store important items or events in memory based on their goals.  Working memory and episodic memory systems are responsible for this remarkable ability.

@@

%visual reasoning~\cite{mogadala2019trends} - datasets such as COG~\cite{yang2018dataset} and 
%SVQA (Synthetic Video Question Answering)~\cite{song2018explore}
%
%
%ARISTO project~\cite{clark2019f} - based on RoBERTa~\cite{liu2019roberta} contextual word embeddings
%
%transformer-based solutions~\cite{vaswani2017attention} using self-attention
%
%
%“The current neural network approaches will find it difficult to determine which combinations of ‘later’, ‘earlier’, ‘more’, and ‘less’ constitute ‘increase’ and which constitute ‘decrease,'” Davis says. “Neural networks have no inherent idea of magnitude or of time.”
%~\cite{davis2016write}

%\begin{itemize}
%\item bAbI:  MemNets~\cite{weston2014memory} have access to the whole story at once
%\item the same goes to SoftPats~\cite{haurilet2019s} - they build graph per frame and then frame number is treated as one dimensions, so at the end the \textit{Traveler} can access all of them at the same time 
%\item The paper~\cite{le2019learning} focuses on SVQA and TGIF-QA -  they access all frames at once, i.e. cut the video into clips, process each frame with CNNs and then aggregate feature representations of equal-size clips obtained by a temporal attention mechanism. So in fact the model has access to all frames all the time.
%\end{itemize}
%so the time aspect is really... not dealt with?
%
%Additionally, in~\cite{song2018explore} the authors introduced a large-scale dataset caled SVQA (Synthetic Video Question Answering) consisting of (Total QA pairs: 83160/11760/23760 and Total Videos 8400/1200/2400).
%As "using all frames is time-consuming. Thus we divide each video into clips (segments) of 16 frames, with 80\% overlap between successive clips (segments)" and "We extract feature from each clip and aggregate features of all clips from one video to form a sequential video representation." -- which means that they identified the problem that you "cannot extract features from all frames" at the beginning and pass that to the model. But instead of proposing a solution that will deal with the video on per-frame basis, they "cheated". ;)
%
%IMPORTANT: \textbf{we do not have any explicit assumptions when it comes to number of frames/length of the movie/number of distractionts}, so there is no need for cutting video into cuts etc.

### 2019-09-14 2019_neurips_vigil/model.tex
Question driven controller first draft

@@

The Question-driven Controller plays an important role in the reasoning process.
it drives the attention over the question and produces the new control states. Each new control state defines a new reasoning operation. The inputs of this unit are the past control state, the question encoding and the contextual words (see Question Encoding Unit). It uses the dot product attention between the contextual words
and the combination of the past control states and the question encoding.  This attention layer produces the new control state.

This unit also output the temporal class weights that will be used in the Reasoning Unit. It gives access to a temporal information for the current words. (last,latest,now, none temporal)

@@

The role of the memory retrievial unit is to read and extract object from memory (Selective AttentionMemory).
As the Visual Retrievial Unit, it uses a combination of two following submodules. The interaction module responsible to blend the extracted object and the content of the memory. The attention module then extract the corresponding object in memory if present.

\subsection{Reasoning Unit}
\subsection{Memory update Unit}
\subsection{Summary Object Udpate Unit}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{../img/architecture/samnet_architecture}
	\caption{}
	\label{fig:samnetarchitecture}
\end{figure}

@@

The Question-driven Controller plays an important role in the reasoning process.
It drives the attention over the question and produces the new control states. Each new control state defines a new reasoning operation. The inputs of this unit are the past control state, the question encoding and the contextual words (see Question Encoding Unit). It uses the dot product attention between the contextual words
and the combination of the past control states and the question encoding.  This attention layer produces the new control state.

This unit also output the temporal class weights that will be used in the Reasoning Unit. It gives access to a temporal information for the current words. (last, latest, now, none temporal)

@@

The role of the memory retrieval unit is to read and extract object from memory (Selective Attention Memory).
As the Visual Retrieval Unit, it uses a combination of two following submodules. The interaction module responsible to blend the extracted object and the content of the memory. The attention module then extract the corresponding object in memory if present.

\subsection{Reasoning Unit}

\subsection{Memory update Unit}

This unit is meant to update the content of the memory. It is controlled by two booleans that decides if the object needs to be added to a new position, or replaced somewhere. 
It also updated the position of the write head. If a new object as been added to the current write head position, the right head shifts right to a new empty slot. If the object has been replaced, the write head doesn't move.

\subsection{Summary Object  Unit}

The goal of the Summary Object
